---
title: "T-Test"
author: "Carmen Garcia-Russell"
date: '2023-03-02'
output:
  html_document:
    theme: darkly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

When testing to see if participants saw a difference in skin hue a t-test was run and there was on average a significant difference on the perception between the dark-skinned mug shot (M=5.07, SE = 0.29), and the light-skinned mug shot (M= 3.84, SE = 0.29). This difference, 1.23, 95% CI[0.59, 0.6] was significant p = 0.004.

In other words, this study was set up well, and if done with a larger sample population may have different results. People did see a difference in the mugshot's skin hue. They rated the original photo at 3.84 and the dark-skinned mugshot at at 5.07.

```{r echo=FALSE}
Number <- tribble(~ Ethnicity, ~ Number,
                   "Hispanic", "42",
                  "Non Hispanic", "29")

#Graph
ggplot(Number,
       aes(x = Ethnicity, y = Number)) +
  geom_bar(stat = "identity",
           fill = "darkgreen") +
labs(title = "Demographics",
       y="Sample Population", x="Ethnicity")

```

